### 2017-11-01 Maths Notes/S2/Hypothesis testing/Hypothesis testing.tex
Initial upload of all files

\begin{document}
\begin{center}
\underline{\huge Binomial and Poisson Distributions}
\end{center}
\begin{obeylines}
\section{The Binomial Distribution}
\subsection{Introduction to the binomial distribution}
The binomial distribution is a \textbf{discrete} distribution.
Conditions for a binomial distribution:
\begin{itemize}
\item There are a fixed number of trials, \textbf{n}
\item There are two outcomes (success and failure)
\item Each trial is independent
\item The probability of success is constant, \textbf{p}
\end{itemize}
Formula:
For $X~B(n,p)$

$P(X=r)=\binom{n}{r}p^r(1-p)^{n-r}$

Example:
If 25 dice are thrown, find the probability three sixes are obtained.
$X~B(25,\frac{1}{6})$
$P(X=3)=\binom{25}{3}(\frac{1}{6})^3(\frac{5}{6})^{22}=0.1929$
\subsection{Use of tables}
Tables give "less than or equal to" probabilities.

Example:
$X~B(5,0.35)$
$P(x\leq3)=0.9640$ (in the table where n=5, p=0.35 and x=3)
$P(x<4)=0.9640$ (the data is discrete)
$P(x=3)=P(x\leq3)-P(x\leq2)$
$P(x=3)=0.9640-0.7648$
$ $
$P(x\geq3)=1-P(X\leq2)$
$P(x\geq3)=1-0.7648$
$P(x\geq3)=0.2352$
\subsection{Dealing with $P>\frac{1}{2}$}
Example:
In the production of a car it is found that 85 \% are without defects.
The cars are produces in batches of 50
\textit{Find the probability there are at least 40 defect-free cars in a batch}
X=Number of cars without defects
$X~B(50,0.85)$
$P(X\geq40)$
Y=Number of cars with defects
$Y~B(50,0.15)$
$P(Y\leq10)=0.8801=P(x\geq40)$
\subsection{Mean and variance of the binomial distribution}
$E(X)=np$
$Var(x)=np(1-p)$
$\sigma(x)=\sqrt{Var(x)}$
Example 1:
$X~B(80,0.4)$ \textit{Find $E(x)$ and $\sigma$}
$E(x)=80\times0.4=32$
$\sigma=80\times0.4(1-0.4)=4.38$
$ $
\newpage
Example 2:
$E(x)=8$
$Var(x)=6.4$
\textit{Find n and p}
$np-np^2=6.4$
$8-np^2=6.4$
$np^2=1.6$
$ $
$p=\dfrac{np^2}{np}=\dfrac{1.6}{8}=0.2$
$ $
$n=\dfrac{np}{p}=\dfrac{8}{0.2}=40$
\section{The Poisson Distribution}
\subsection{Introduction to the Poisson Distribution}
The conditions for a poisson distribution are:
\begin{itemize}
\item Events occur at random
\item Events occur independently of each other
\item The average rate of occurrences remains constant
\item There is zero probability of simultaneous occurrences 
\end{itemize}
$P(x=r)=\dfrac{e^{-\lambda}\lambda^r}{r!}$
$\lambda$ represents the mean number of occurrences in the time period.
\textbf{Example}
$x\sim P_o(4)$
$P(x=2)=\dfrac{e^{-4}\times 4^2}{2!}=0.1465$
\subsection{Mean and variance of the poisson distribution}
If $X~P_o(\lambda)$ then $E(x)=\mu=\lambda$ and $Var(x)=\lambda$
\subsection{Using the Poisson as an approximation of the binomial}
You can use the Poisson distribution as an approximation if:
\begin{itemize}
\item P is small $(<0.1)$
\item n is large $(>50)$
\end{itemize}
$\lambda=np$
$X\sim B(n,p)\approx Y\sim P_o(np)$
\textbf{Example}
$X\sim B(250,0.01)\approx X\sim P_o(2.5)$

\end{obeylines}
\end{document}

>>>>

\begin{document}
\begin{center}
\underline{\huge Hypothesis testing}
\end{center}
\section{Tests of hypotheses}
\textbf{Statistical hypothesis} - An assertion or conjecture concerning a population.\\
\\
To test the validity of a statement a random sample is taken from the population and that data can them be used to provide evidence that either supports or does not support the hypothesis.\\
\\
\textbf{Null hypothesis} - $H_0$ - A hypothesis assumed to be true
\textbf{Alternative hypothesis} - $H_1$ - The situation if $H_0$ is false.

If the data leads to rejection of the null hypothesis the alternative hypothesis will be accepted.

The sample data is used to evaluate the \textbf{test statistic}, probabilities related to it can be calculated using the null hypothesis.

Critical values are the range of values that if the test statistic is found in the null hypothesis will be rejected.

\end{document}
